---
title: "Calculate Total Trackline Distance"
output: html_notebook
---


```{r}
.packageName<-"argosfilter"

`distanceTrack` <-
function(lat, lon)
{
distanceTrack<-numeric(length(lat)-1)
for (k in 1:(length(lat)-1)){
	lat1<-lat[k]
	lat2<-lat[k+1]
	lon1<-lon[k]
	lon2<-lon[k+1]
	distanceTrack[k]<-distance(lat1,lat2,lon1,lon2)
	}
distanceTrack
}
```


Total trackline tracked with the acoustics GPS, which needs to be paired down by effort and time of day.
```{r}
library(lubridate)

gps <- read.csv('C:\\Users\\Yvonne\\Documents\\PHD\\CHP2&3-Sperm\\data\\All GPS Data\\GPS_1303_raw - Copy.csv')

gps <- read.csv('C:\\Users\\Yvonne\\Documents\\PHD\\CHP2&3-Sperm\\data\\All GPS Data\\GPS_1604_edit.csv')

gps <- read.csv('C:\\Users\\Yvonne\\Documents\\PHD\\CHP2&3-Sperm\\data\\All GPS Data\\GPS_1705_raw.csv')
gps <- read.csv('C:\\Users\\Yvonne\\Documents\\PHD\\CHP2&3-Sperm\\data\\All GPS Data\\GPS_1706_raw.csv')

#subset for correct gps values, using Latitude is easiest
gpssub <- subset(gps, (Latitude > 15 & Latitude < 32 ))

#gpssub$UTC <- as.character(gpssub$UTC)

gpssub$UTC <- as.POSIXct(as.character(gpssub$UTC), "%Y-%m-%d %H:%M:%S")#, tz="UTC")

#1604 is problem dataset for date-time
gpssub$UTC <- as.POSIXct(strptime(as.character(gpssub$UTC), "%m-%d-%Y %H:%M:%S"))

#add column for distances
gpssub$distance <- NA
gpssub$distance[2:nrow(gpssub)] <- distanceTrack(gpssub$Latitude, gpssub$Longitude)

#sum the distances in km
SE1303=sum(gpssub$distance[2:nrow(gpssub)])
SE1604=sum(gpssub$distance[2:nrow(gpssub)])
L1705=sum(gpssub$distance[2:nrow(gpssub)])
SE1706=sum(gpssub$distance[2:nrow(gpssub)])
```

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
